\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}


\hspace{0.6cm}Recruitment management is a critical aspect for any organization 
aiming to maintain its competitiveness in the job market. In this project conducted at the National
 Institute of Posts and Telecommunications (INPT) in software engineering, we undertook the design and development
  of a recruitment management platform for the company 4D. This platform aims to streamline and automate various stages of the recruitment process, from candidate sourcing to onboarding.
\newline

The project involved several key phases, including a thorough analysis of the company's needs, the design of a suitable software architecture, the development of customized features, and the implementation of tracking and evaluation tools. By utilizing best practices in software development and the latest technologies, we were able to create a robust and scalable platform capable of meeting the specific requirements of company 4D.
one of them.
\newline

The main features of the platform include job offer management, automatic distribution across various recruitment channels, candidate management, interview tracking, collaboration among different stakeholders in the recruitment process, and the generation of analytical reports to assess the effectiveness of implemented recruitment strategies.
Science.
\newline

This project provided an opportunity to apply theoretical knowledge gained during our software engineering training at INPT and develop essential skills in designing and developing software solutions. It also represents a significant contribution to optimizing the recruitment processes of company 4D, enabling more efficient and transparent human resource management.
\newline




\vspace{1cm}
\noindent\rule[2pt]{\textwidth}{0.5pt}
\textbf{Keywords :} Recruitment, Management, Application, Software Engineering, Platform Development, Company 4D, Process Optimization, Job Offers, Interview Tracking.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \pagestyle{empty}\strut \null
