\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This report presents the work carried out during my end-of-studies internship at 4D Software Morocco, focused on the design and development of a recruitment management platform. The agile methodology was adopted, with rapid iterations and continuous adjustments based on needs, given the absence of a well-defined specification document.
\newline

The main objective of this project is to simplify and automate the recruitment process, thereby reducing processing times and efforts by recruiters. This will be achieved by integrating advanced features, including job offer management, automatic CV sorting, candidate skill evaluation through assessment tests, and interview scheduling into a single coherent system.
\newline

To successfully complete this project, we followed several steps. First, an in-depth needs analysis was conducted to identify the specific requirements of candidates, recruiters, and administrators. Next, the system modeling was carried out using UML and BPMN diagrams. Finally, the development of features was undertaken, primarily based on the 4D backend language, while integrating tests to ensure the quality and reliability of the final product.
\newline


\vspace{1cm}
\noindent\rule[2pt]{\textwidth}{0.5pt}
\textbf{Keywords :} Recruitment, Management, Application, Software Engineering, Platform Development, Company 4D, Process Optimization, Job Offers, Interview Tracking.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \pagestyle{empty}\strut \null
